### 2016-02-22 paper.tex
Compare performance results with SAFL; resolves #35

The behavior of the power and drag coefficients at $\lambda=3.1$ are plotted in
Fig.~\ref{fig:perf-re-dep}, where we can see a Reynolds number independent value
of $C_D$ was observed. The power coefficient of the turbine increases
dramatically below $Re_D = 1 \times 10^6$ or $Re_c \equiv \lambda U_\infty c /
\nu \approx 2 \times 10^5$, beyond which there appears to be a small, linear,
positive trend. At the lowest Reynolds number, mean power coefficient even drops
below zero, which is consistent with the low performance of the 1:15 scale RM2
physical model study~\cite{Hill2014}.

>>>>

The behavior of the power and drag coefficients at $\lambda=3.1$ are plotted in
Fig.~\ref{fig:perf-re-dep}, where we can see a Reynolds number independent value
of $C_D$ was observed. The power coefficient of the turbine increases
dramatically below $Re_D = 1 \times 10^6$ or $Re_c \equiv \lambda U_\infty c /
\nu \approx 2 \times 10^5$, beyond which there appears to be a small, linear,
positive trend. At the lowest Reynolds number, mean power coefficient even drops
below zero, which is consistent with the low performance of the 1:15 scale RM2
physical model study~\cite{Hill2014}. However, the blades of the 1:15 scale RM2
were mounted at approximately 58\% of the chord from the leading edge, versus
50\% for the present model, which helps explain the 1:15 scale model's positive
power output at $\lambda=2.2$ and $Re_D \sim 10^5$, since moving the blade mount
point further back is equivalent to a ``toe-out'' preset pitch
condition~\cite{Fiedler2009}.
